\documentclass{article}

\begin{document}

\section{Introooduction}

It was a cold Sunday evening on the UC Berkeley Campus. The clock struck 8
o'clock PM. Calvin came from his dorm room. Jamila came from her home.
Jusheen came from an economics review session. All racing to meet up in Moffitt
and finish their data science decal project.

\section{The Plot Twist}

Once they finished up the logistics, Calvin walked back to his dorm to chill and
relax before taking on the new week once again. On his way back though, he got
some bread and other foods from the Shengkee Bakery for tomorrow's breakfast, and
decided that two buns would be enough to get him through his morning lecture the
next morning. After that, he briskly walked back to his dorm (Unit 2 Ehrman), and
got to see his roommates and play a couple online video games before hitting the hay.
They played a couple matches of NBA Jam, and Calvin obviously beat both of his
roommates. He then prepped to sleep by brushing his teeth, washing his face, and
taking a shower. By then, he was completely pooped and went to bed for a good
night's sleep.

The next morning, Calvin walked up and decided to go to class, where he found
that he slept through the entire semester! He didn't realize that he was that tired,
to be able to sleep through 9 straight weeks, but somehow, someway, he did. His
first reaction was to check what happened to his grades in his classes, as he suspected
that he'd be on academic probation at that point. Turns out, he got straight A+'s in
all of his classes! It was both incredibly surprising and pleasing to know that
despite his irrationally large amount of sleep, he was still able to maintain good
grades and not be kicked out of UC Berkeley, the number 1 Public University of the World
behind UCLA (haha just kidding we all know that bears are >>> than bruins). He
realized his incredibly good fortune, and believed that because he was so incredibly
lucky right now, he might as well just buy a lottery ticket and see what happens.
After all, winning the lottery would probably be more likely to occur than it is to
sleep through 9 weeks and somehow achieve perfect grades in all of his classes.
So, later on, when he was looking at the lottery numbers on the TV screen, they were
all beginning to match the numbers on his ticket. "7, 9, 15, 34, and..." And then
he woke up. Time to really start school.


\end{document}
