\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}

\section{Introduction}
It was a cold Sunday evening on the UC Berkeley Campus. The clock struck 8 o'clock PM. Calvin came from his dorm room. Jamila came from her home. Jusheen came from an economics review session. All racing to meet up in Moffitt and finish their data science decal project.

\section{Jamila}
Jamila was struggling with git, especially remembering git commands. So with the help of her teammates Calvin, Jusheen, and the internet she was able to learn so much. In the span of two hours, her teammates and the Internet taught her all she needed to understand and get started with the data science git project. The next morning, Jamila woke up and was feeling accomplished but too lazy to begin her project. Jamila also worried that if she put the project off for too long she may forget some of the material or worse have no time to finish it. Jamila had a busy day that Monday. She had to meet up with her counselor, finish a project for another class, and finish an op-ed paper for another class. Jamila, stressed about her day, gets a call from her friend Alex. Alex had a big argument with her parents over her poor grades, and was struggling emotionally. Jamila and Alex have known each other for a long time and were very close. Jamila was worried that Alex would be alone and unable to cope with this fight. Jamila decided that she would try to finish most of her homework before she met up with Alex. Jamila was able to complete her project and op-ed. It was 7 PM and she still had not completed her data science git project. Jamila decided she would meet up with Alex and spend time with her and later she would finish her data science project. Jamila arrives in Alex’s apartment. Jamila and Alex talk and Jamila tries to give her advice and reassure her that things will get better. Jamila leaves Alex’s apartment, heads home, and finally finishes her git project. 
\end{document}
