\documentclass{article}

\begin{document}

\section{Introduction}
It was a cold Sunday evening on the UC Berkeley Campus. The clock struck 8 o'clock PM. Calvin came from his dorm room. Jamila came from her home. Jusheen came from an economics review session. All racing to meet up in Moffitt and finish their data science decal project.

\section{jusheen Version}

Once Jusheen had to leave, he left to go to a couple floors up above in moffit library. There he met his CS partner to work on the dreaded project 2 of CS 61B. Ju Sheen is very bad at CS so he and his partner struggled with the project. They are worked on a world generation algorithm that involves a lot of writing code. The code they are using is java.
The pair worried and worried until jusheen decided to go home and sleep. jusheen then proceeded to sleep for 13 hours. he missed all his morning classes and showed up late to his last class of the day. he felt very proud of going to class that day, as he usually misses most of his classes everyday, unless they are very late at night like this decal.
He then went to the gym and worked out chest and triceps. he worked out with his friend, who also worked out chest and triceps. jusheen began to incorporate isolation exercises into his routine to ensure symmetrical bilateral muscular development. He doesnt want his right side or left side to become bigger than the other, so he makes sure to develop
a mind-muscle connection. He took this advice from the legendary bodybuilder Kai Greene, aka mr getting it done aka the predator. Kai is very big, and jusheen is not. jusheen wants to get big, but not as big as kai. jusheen cannot get as big as kai anyway because kai takes steriods and hgh but jusheen is a lifetime natural bodybuilder.


\end{document}
